Supplemental material for `Eliminating object prior-bias from sparse-projection tomographic reconstructions'

### 2021-10-15 paper/post_tci_supplementary.tex
Added videos
minor changes of adding *

\begin{itemize}
\item \textbf{Okra:}

  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}
\item \textbf{Potato:}

@@

  \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}
\end{itemize}

@@

We mention in passing that if we are to entirely avoid the other
parameters (viz. $\lambda_1$ and $\lambda_2$), the prior and the pilot
can be stitched in a simplistic way using the equation 
$\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
The advantage of this method is that the computational time is
signficantly reduced since the alternate minimization procedure is not
used.

>>>>

\begin{itemize}

\item \textbf{Potato:}

@@

    \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}

  \item \textbf{Okra:}

  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}
\end{itemize}

@@

We mention in passing that if we are to entirely avoid the other
parameters (viz. $\lambda_1$ and $\lambda_2$), the prior and the pilot
can be stitched in a simplistic way using the equation 
$\boldsymbol{W_b}*(\rm{pilot}) + (1-\boldsymbol{W_b})*(\rm{prior})$.
The advantage of this method is that the computational time is
signficantly reduced since the alternate minimization procedure is not
used.
